Efficient Coalition Formation for Web Services

### 2013-03-15 papers/coalition/coalition.tex
Changes

We first analyze the most important performance result our communities should perform, quality and quantity of tasks successfully performed by our communities. This is the most important criteria for user satisfaction. We initiate the community with few web services, then let rejecting and accepting of random web services go for a while, after that we start task distribution for the communities and let them allocate tasks for web services. Then we measure the average output performance of tasks in communities following different methods.

@@

Figure \ref{performanceall} depicts the results of simulation of optimal \emph{$\epsilon$-core} with 10\% of total community value deviation allowed (one grand community with many web services), \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, 3-Way Satisfactory\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative} methods. The the \emph{optimal $\epsilon$-core} method we capped the coalition size to 24 web services, since anything more than that would require analysis with time complexity of $O(2^{24-1})$, making it impractical to run in our simulations. In other methods there were no cap on size of the community and we had communities of size 60 web services at some points. The results show \depth{depth-2 and 1 convex checker} methods are performing well compared to other methods and all not far from optimal.

@@

As mentioned in section \ref{s:preliminaries}, core assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of \emph{$\epsilon$-core} was introduced. Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty. We evaluated the least-core value using our valuation function and our set of web services. We pick random number of web services from our data set and formed around 10,000 random coalitions consisting of 3 to 25 web services. We choose 25 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$-core}. We set $\epsilon$ to a ratio of total payoff of coalition $v(C)$ between 0 and 1. The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty core solution and \emph{$\epsilon$-core} solution is always non-empty when we let agents gain only 30\% (of $v(C)$) more, by deviating.

>>>>

We analyze the most important performance result the communities should perform, quality and quantity of tasks successfully performed by the communities. This is the most important criteria for user satisfaction. We initiate the community with few web services, then let rejecting and accepting of random web services go for a short number of iterations, after that we start task distribution for the communities and let them allocate tasks for web services. Then we measure the average output performance of tasks in communities following different methods.

@@

Figure \ref{performanceall} depicts the results of optimal \emph{$\epsilon$-core}, by assigning $\epsilon$ to 15\% of total community worth, $\epsilon = 0.15 \times v(C)$, allowing subsets of coalition to gain maximum 15\% of $v(C)$, \emph{Depth-1 Convex-Checker}, \emph{Depth-2 Convex-Checker}, \emph{3-Way Satisfactory}\cite{DBLP:conf/IEEEscc/LimTMB12} and \emph{2 Player Non-Cooperative}\cite{DBLP:conf/IEEEscc/KhosravifarABT11} methods in \emph{one grand community with many web services} scenario. In the \emph{optimal $\epsilon$-core} method we capped the coalition size to 25 web services, since anything more than that would require analysis with time complexity of $O(2^{n-1})$, making it impractical to run in our simulations. In other methods there were no cap on size of the community and we had communities of size 60 web services at some points. The results show \emph{depth-2 and 1 convex checker} methods are performing better compared to other methods and their performance is close to optimal \emph{$\epsilon$-core} method.

@@

As mentioned in section \ref{s:preliminaries}, the concept of \emph{core}, assumes no coalition of players can gain anything by deviating which is a fairly strong requirement, that is why the notion of \emph{$\epsilon$-core} was introduced. Least-Core $e(G)$ of a game $G$, is the minimum amount of $\epsilon$ in which the core is not empty. We evaluated the least-core value using our valuation function and our set of web services. We pick random number of web services from our dataset and formed around 10,000 random coalitions consisting of 3 to 26 web services. We choose 26 as maximum number of members in our grand coalition since it is computationally very complex for bigger coalitions to compute \emph{$\epsilon$-core}. We set $\epsilon$ to a ratio of total payoff of coalition $v(C)$ between 0 and 1. The results in figure \ref{f_leastcore} illustrates, almost 10\% of our random web service coalitions have non-empty \emph{core} solution and \emph{$\epsilon$-core} solution is \emph{always} non-empty when we let agents gain 30\% (of $v(C)$) more, by deviating.
